Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-22 paper.qmd
Updated Figure 2 title

```{r}
#| label: fig-two-curvy-true-proj
#| fig-cap: "Two projections from $7\\text{-}D$, for the two non-linear clusters data are shown. The sample obtained from the true model is shown, with the sample shown in grey and the true model in blue lines. In the C-shaped cluster, the data points are distributed randomly along the cluster, while the data is more concentrated more in one corner in the other non-linear cluster. Video of the langevitour animations are available at <>." 
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5

@@

<!--add langevitour screenshots and youtube animation link-->
```{r}
#| label: fig-mnist-tri-proj
#| fig-pos: H
#| fig-height: 4
#| fig-width: 12
#| out-height: 100%
#| fig-cap: "\\gD{} wireframe layout shows that there is a big non-linear cluster (grey) and a small cluster (orange) located very close to the one corner of the big cluster. The MNIST digit 1 data ($n =  7877$ and $p = 10$) has a non-linear structure in $10\\text{-}D$. Two \\gD{} projection from a tour on $10\\text{-}D$ reveal that the closeness of the clusters in $10\\text{-}D$ and the twisted pattern of the model fit with tSNE ($a_1 = 0.041$, $b = 659/585 \\text{ } (30, \\text{ }48)$). Video of the langevitour animation is available at <>."

>>>>

```{r}
#| label: fig-two-curvy-true-proj
#| fig-cap: "Two \\gD{} projections from $7\\text{-}D$, for the two non-linear clusters data (grey points) and true model (blue lines) are shown. The top cluster in (a) shows uniformly distributed data along a C-shape, while in the bottom cluster, the data is more concentrated in one corner of the curvy shape. Video of the langevitour animations are available at <>." 
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5

@@

<!--add langevitour screenshots and youtube animation link-->
```{r}
#| label: fig-mnist-tri-proj
#| fig-pos: H
#| fig-height: 4
#| fig-width: 12
#| out-height: 100%
#| fig-cap: "\\gD{} wireframe layout shows that there is a big non-linear cluster (grey) and a small cluster (orange) located very close to the one corner of the big cluster. The MNIST digit 1 data ($n =  7877$ and $p = 10$) has a non-linear structure in $10\\text{-}D$. Two \\gD{} projections from a tour on $10\\text{-}D$ reveal that the closeness of the clusters in $10\\text{-}D$ and the twisted pattern of the model fit with tSNE ($a_1 = 0.041$, $b = 659/585 \\text{ } (30, \\text{ }48)$). Video of the langevitour animation is available at <>."
